\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}

\emph{ }\\
In front of you lies the master thesis ‘Rotterdam’s Groundwater Monitoring Network: A Critical Examination of the Groundwater Monitoring Network and its Optimization Potential’. This master thesis has been written to fulfill the graduation requirements of the double degree program Transnational ecosystem-based Water Management at Radboud University Nijmegen, The Netherlands, and University Duisburg-Essen, Germany. My research and writing for this thesis spanned from September 20, 2023, to April 9, 2024.
\newline
\newline
This thesis highlights the remarkable moment of submitting my master thesis on April 9 2024, when I started my initial master thesis exactly one year ago. Due to unfortunate circumstances the thesis was paused. I am very grateful I could continue the end phase of my studies at Gemeente Rotterdam on the topic of geohydrology.
\newline
\newline
I would like to thank my in-company supervisors Bert de Doelder and Koen Geul for their guidance and support during the process. As well as Mattijs Borst from CWG Engineers who supported me, together with Koen Geul, to take the step to start learning the programming language Python. This step greatly benefited the quality of the research study. Additionally, all the colleagues at the department of Urban Water, supported me during the writing process. Furthermore, external guidance from Deltares and the Bewonersorganisatie Hillegersberg-Schiebroek. Lastly, Dr. Gertjan Geerling as first assesor from Radboud University Nijmegen/Deltares and second assessor Dr. Ekkehard Christoffels from University Duisburg-Essen/IBC Ingenieure for their participation.
\newline
\newline
Finally, many thanks to my family and friends who supported me throughout the 2.5 years of the masters program. 
\newline
\newline
Enjoy your reading.
\bigskip

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Rotterdam, \monthname{} \the\year{}
\makeatother}
\end{flushright}
